---
title: "Iteration and List Columns"
author: "Jessica Lavery"
date: "10/29/2019"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

set.seed(1)
```

## Lists
```{r}
l <- list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
```

### Accessing components of a list
```{r}
l$vec_numeric

# same result as above
l[1]

# TBD what the difference is between [] and [[]], use [[]]
l[[1]]

# pull out specific elements
l[[1]][1:3]
```


```{r}
df <- list(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

# mean (SD) function from last class
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

#compute mean (SD) for each column in df
# have to use double brackets here
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
mean_and_sd(df[[3]])
mean_and_sd(df[[4]])

# instead of calling mean_and_sd 4x, write as a for loop
output = vector("list", length = 4)
output #4 blank spots

# for loop
for (i in 1:4) { 
  output[[i]] = mean_and_sd(df[[i]])
  }

# now output is populated with the results from the for loop
output
class(output)

# change for loop into a map statement 
output2 = map(df, mean_and_sd)
output2

# to get the median instead
output_median = map(df, median)
output_median

# to get a summary instead
output_summary = map(df, summary)
output_summary

# using map_dfr to return a data frame instead of a list
output_df = map_dfr(df, mean_and_sd, .id = "input")
class(output_df)
```

## Using the map function to iterate over pages when scraping data from the web

```{r}
# function to read page reviews based on URL
read_page_reviews = function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  data_frame(title, stars, text)
}

# create a vector of URLs for which we want to pull reviews from
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

# str_c concatenate strings 
vec_urls = str_c(url_base, 1:5)

# first, try to write for loops
# create empty slots for the output
output = vector("list", length = 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

output

# via map
output = map(vec_urls, read_page_reviews)
```

## List columns (RNOAA dataset)

```{r}
weather = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2016-01-01",
    date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Nest within weather stations

The `nest` function creates list columns within the nest levels provided.

From documentation: Nesting creates a list-column of data frames; unnesting flattens it back out into regular columns.

```{r}
weather_nest = 
  nest(weather, data = date:tmin)

weather_nest

# name is the summarized character column
weather_nest %>% pull(name)

# is the list column really a list?
# column data is the list column
weather_nest %>% pull(data)
class(weather_nest %>% pull(data))

# can also unnest things
# weather_nest %>% unnest(cols = c(data))
```

### Can I do useful things with a list column?

Can use list columsn to run stratified model. 

```{r}
central_park_df <- weather_nest$data[[1]]
central_park_df

# fit a linear model
lm(tmax ~ tmin, data = central_park_df)

# want to automate this across all three places that we have weather data on so that we don't have to copy/past 3x
lm(tmax ~ tmin, data = weather_nest$data[[1]])
lm(tmax ~ tmin, data = weather_nest$data[[2]])
lm(tmax ~ tmin, data = weather_nest$data[[3]])

# try a for loop
output = vector("list", length = 3)

for (i in 1:3) {
  output[[i]] = lm(tmax ~ tmin, data = weather_nest$data[[i]])
}

output

# try to write a function instead of a for loop
weather_lm = function(df){
  lm(tmax ~ tmin, data = df)
}

# now in for loop could use this function instead
for (i in 1:3) {
  output[[i]] = weather_lm(weather_nest$data[[i]])
}
output

# now move to a map statement 
output_map = map(weather_nest$data, weather_lm)

# now have 1 output for each data frame (location) that you're interested in
output_map

# add a column with information from linear models
weather_nest_models <- weather_nest %>% 
  mutate(lin_models = map(data, weather_lm)) %>% 
  select(-data) %>% 
  filter(name != "CentralPark_NY")
```


## Revisit Napoleon

```{r}
# get tibble with 
napoleon <- tibble(page = 1:5,
                   urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest(reviews)
```


